The importance of measurement uncertainty in ecological management

### 2018-02-01 manuscripts/manuscript.tex
220 word abstract only

  \begin{abstract}
  Ecological management and decision-making typically focus on uncertainty
  about the future, but surprisingly little is known about how to account
  for uncertainty of the present: that is, the realities of having only
  partial or imperfect measurements. Our two primary paradigms for
  handling decisions under uncertainty -- the precautionary principle and
  optimal control -- have so far given entirely controdictory results.
  This paradox is best illustrated in the example of fisheries management,
  where many ideas that guide our thinking about ecological decision
  making were first developed. There, we find that simplistic optimal
  control approaches have repeatedly concluded that a manager should
  increase catch quotas when faced with greater uncertainty about the
  standing stock biomass. Meanwhile, most current best practices take a
  more precautionary approach, decreasing catch quotas by a fixed amount
  to account for uncertainty. Using comparisons to both simulated and
  historical catch data, we find that neither approach is sufficient to
  avoid stock collapses under moderate observational uncertainty. Using
  cutting-edge point-based partially observed Markov decision process
  (POMDP) methods, we demonstrate how this paradox arises from flaws in
  the standard management theory, which contributes to over-exploitation
  of fisheries and increased probability of economic and ecological
  collapse. In contrast, we find POMDP-based management avoids such
  over-exploitation while also generating higher economic value through
  adaptive learning. These results have significant implications for how
  we handle uncertainty in both fisheries and ecological management more
  generally. Dealing with uncertainty in decisions requires approaches
  which are both adaptive and explicit about uncertainty, such as POMDPs.
  \end{abstract}
   \begin{keyword} Measurement uncertainty \sep POMDP \sep Decision theory \sep Fisheries \sep Conservation \sep \end{keyword}
 \end{frontmatter}

>>>>

  \begin{abstract}
  Ecological management and decision-making typically focus on uncertainty
  about the future, but surprisingly little is known about how to account
  for uncertainty of the present: that is, the realities of having only
  partial or imperfect measurements. Our two primary paradigms for
  handling decisions under uncertainty -- the precautionary principle and
  optimal control -- have so far given entirely contradictory results.
  This paradox is best illustrated in the example of fisheries management,
  where many ideas that guide thinking about ecological decision making
  were first developed. We find that simplistic optimal control approaches
  have repeatedly concluded that a manager should increase catch quotas
  when faced with greater uncertainty about the fish biomass. Current best
  practices take a more precautionary approach, decreasing catch quotas by
  a fixed amount to account for uncertainty. Using comparisons to both
  simulated and historical catch data, we find that neither approach is
  sufficient to avoid stock collapses under moderate observational
  uncertainty. Using partially observed Markov decision process (POMDP)
  methods, we demonstrate how this paradox arises from flaws in the
  standard theory, which contributes to over-exploitation of fisheries and
  increased probability of economic and ecological collapse. In contrast,
  we find POMDP-based management avoids such over-exploitation while also
  generating higher economic value. These results have significant
  implications for how we handle uncertainty in both fisheries and
  ecological management more generally.
  \end{abstract}
   \begin{keyword} Measurement uncertainty \sep POMDP \sep Decision theory \sep Fisheries \sep Conservation \sep \end{keyword}
 \end{frontmatter}
